
---
title: "GR5320 Project"
output: html_notebook
---


### Step 1: Load Data (Equities in Portfolio)
We download our data from "Yahoo Finance" by using "tidyquant" package. Users can choose any tickers they want.
Here,for mathematical descriptions of model, we use "XOM"&"INTC" as example.
```{r,message=FALSE}
library(ggplot2)
library(MASS)
library(quantmod)
if (!require("quantmod")) {
    install.packages("quantmod")
    library(quantmod)
}
if (!require("tidyquant")) {
    install.packages("tidyquant")
    library(tidyquant)
}
```

```{r}
XOM <- read.csv("../data/XOM-bloomberg.csv")
INTC <- read.csv("../data/INTC-bloomberg.csv")

XOM$Dates <- as.Date(XOM$Dates,"%m/%d/%Y")
INTC$Dates <- as.Date(INTC$Dates,"%m/%d/%Y")
```

**Tickers**
```{r}
XOM <- tq_get("XOM", get = "stock.prices",from="1990-01-01")
INTC <- tq_get("INTC", get = "stock.prices",from="1990-01-01")
```

**Options**
```{r}
imp_vol <- read.csv("../data/volatility.csv")
imp_vol$Date <- as.Date(imp_vol$Date,"%m/%d/%Y")
```

### Step 2: Source function and fiels 
```{r}
# calculate parameter for stocks/portfolio return
source("../code/parameter/winEstGBM.R")
source("../code/parameter/expEstGBM.R")
source("../code/parameter/winEstGBM2.R") #estimated parameters and rho for two stocks

# historical VaR/ES
source("../code/stock/HVaR.R") #for individual stock & two stocks
source("../code/stock/HES.R")  #for individual stock & two stocks

# monte carlo VaR/ES
source("../code/stock/MC_update.R")  #for individual stock

source("../code/corrbmsampset.R")   #generate random numbers of brownian motion
source("../code/corrgbmsampset.R")  #for two stocks

# Parametric VaR/ES
source("../code/stock/gbmVaR.R")  #for individual stock
source("../code/stock/gbmES.R")   #for individual stock
source("../code/stocks_parametricVaR.R") #for two stocks

# plot graph
source("../code/plotGraph.R")

#others
source("../doc/calculation_measure.R")

# Backtest
source("../code/BackTest.R")
```


### Step 3: Individual Stock Analysis

#### 3.0: Prepare Inputs
```{r}
s1 <- XOM$adjusted
s2 <- INTC$adjusted
dRtn <- 5                                #horizon for day,eg:5 day VaR
year <- 5                                #window length, 5 years
par1 <- winEstGBM(s1,dRtn,year)          #estimated mu and sigma of stock prices
par2 <- winEstGBM(s2,dRtn,year)
s0 <- 10000                              #$10,000 dollar position each day
```

#### 3.1: Calculate Individual Stock VaR
```{r,warning=FALSE}
# historical VaR  
Hvar <- HVaR_S(s1,0.99,dRtn,year,s0)
plotGraph(Hvar,XOM$date)

# paramentric VaR
Gvar <- gbmVaR(s0,par1$mu_gbm,par1$sigma_gbm,0.99,dRtn)
plotGraph(Hvar,XOM$date)
plotGraph(Gvar,XOM$date)
plotGraph(MVaR,XOM$date)

#Backtest
BT<-BackTest(s1,Gvar,5,10000)
plotGraph(BT,XOM$Dates)


# Monte Carlo VaR
MVaR <- MCVaR(s0, par1$mu_gbm, par1$sigma_gbm, p, dt, npaths,years,dRtn)
plotGraph(MVaR,XOM$date)
```


### Step 4: Portfolio Analysis

#### 4.1: Part 1: Portfolio = weight1*s1 + weight2*s2
##### 4.1.1: Prepare Inputs
```{r}
# Inputs Preparation
source("../code/portfolio_price.R")

prices <- comb.col(XOM$PX_LAST,INTC$PX_LAST)
wgt <- c(156/(156+200),200/(156+200))
positions <- c("long","long") 

dRtn <- 5
year <- 5
v0 <- 10000

portfolio_price <- portfolio_px(prices,wgt,positions,v0)
par_p <- winEstGBM(portfolio_price,dRtn,year)
```

##### 4.1.2: Calculate Portfolio VaR
```{r}
# Historical VaR 
port_Hvar <- HVaR_S(portfolio_price,0.99,dRtn,year,v0)
plotGraph(port_Hvar,INTC$Dates)

# Parametric VaR portfolio follows GBM
Gvar <- gbmVaR(v0,par_p$mu_gbm,par_p$sigma_gbm,0.99,dRtn)
plotGraph(Gvar,INTC$Dates)

# Parametric VaR underlying follows GBM
#-- need to revise all code in this part including inputs --#
source("../doc/loadInput.R")
PVaR <- parametricVaR(a,s0,mu,sigma,rho,p,t,v0)
plotGraph(PVaR,INTC$Dates)

# Monte Carlo (more than 2 stocks situations)
```


#### 4.2: Part 2: Portfolio = Stocks + Options
```{r}
add.col<-function(df, new.col) {
  n.row<-dim(df)[1]
  length(new.col)<-n.row
  cbind(df, new.col)
}

colnames(imp_vol) <- c("Dates","PX","IMP_VOL")

imp_vol$Dates <- format(time(imp_vol$Dates))
INTC$Dates <- format(time(INTC$Dates))

merge(imp_vol,INTC[,c(1,6)],by= "Dates",all = T)
```


```{r}
# Inputs Preparation

```


Step 5: Back Test
```{r}

```






############################## Don't Run Below Parts #######################

#########################################################
Step:test part
```{r}
# one approach to load stock dataset
start <- as.Date("2010-01-01")


aple <- Ad(getSymbols("AAPL", src = "yahoo", auto.assign= F, from = start))
intc <- Ad(getSymbols("INTC", src = "yahoo", auto.assign= F, from = start))

stocks <- as.xts(data.frame(AAPL = AAPL[, "AAPL.Close"], MSFT = MSFT[, "MSFT.Close"], 
    GOOG = GOOG[, "GOOG.Close"]))

# useful in plot
chartSeries(returns_AAPL)


dates <- format(time(aple),"%Y-%m-%d")
aple <- data.frame(dates,aple)
length(aple)
length(aple)
```

